Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-16 ms.tex
Completed editing the Introduction.

Motivated by this shortcoming, we have developed a new class of
empirical models that enable galaxies to occupy halos in a manner
that has {\em simultaneous} dependence
upon multiple halo properties \citep{hearin_etal16},
{\em including continuously variable levels of assembly bias}.
Crucially, our implementation is of sufficient computational efficiency
to permit a proper likelihood analysis of the model parameter space.
Armed with this new methodology, in this paper
we revisit the interpretation of luminosity-dependent
galaxy clustering in the Sloan Digital Sky Survey (SDSS) Data Release
7 (DR7) data, analyzed previously by \citet{zehavi_etal11}, in the
context both standard halo occupation models and these new models.

This work presents a re-analysis of the SDSS DR7 data that
overcomes numerous shortcomings of previous studies.
The main improvements accomplished by our approach stem primarily from our
directly populating mock galaxy catalogs into a cosmological simulation,
whereas previous analyses relied upon analytical fitting functions
with parameters calibrated against a suite of simulations.
In direct mock population, delicate issues present in analytic
modeling, such as scale-dependent halo bias and halo exclusion, are treated exactly.
Our approach also provides a natural framework for studying models of assembly bias,
since we can use the exact clustering properties of simulated halos as a function of
any arbitrary halo properties in the catalog. With direct mock population,
systematic uncertainty in the model is limited to
the sample variance of the simulated box,
errors related to insufficient numerical resolution,
and numerical inaccuracies of halo-finding (e.g., over-merging).

In addition to improvements from direct mock population,
the simulation we use is based on the latest Planck cosmological
parameters \citep{planck13}, updating previous work.
Furthermore, many important
differences between this work and the previous analysis by
\citet{zehavi_etal11} result from the fact that the Monte Carlo Markov
Chains used in \citet{zehavi_etal11} did not sufficiently sample the
posterior distribution (Z. Zheng \& I. Zehavi, private communication).  Therefore,
{\em our analysis supersedes previous work even in the case of
standard halo occupation models}.

>>>>

Motivated by this shortcoming, we have developed a new class of
empirical models that enable galaxies to occupy halos in a manner
that has {\em simultaneous} dependence
upon multiple halo properties \citep{hearin_etal16},
{\em including continuously variable levels of assembly bias}.
Crucially, our implementation is of sufficient computational efficiency
to permit a proper likelihood analysis of the model parameter space.
Armed with this new methodology, in this paper
we revisit the interpretation of luminosity-dependent
galaxy clustering in the Sloan Digital Sky Survey (SDSS) Data Release
7 (DR7) data, analyzed previously by \citet{zehavi_etal11}, in the
context of both standard halo occupation models and these new models 
that permit parameterized galaxy assembly bias.

This work presents a re-analysis of the SDSS DR7 data that
overcomes numerous shortcomings of previous studies.
The primary improvements of our approach stem from the fact that we 
directly populate mock galaxy catalogs within a cosmological simulation,
whereas previous analyses relied upon analytical fitting functions
with parameters calibrated against a suite of simulations. 
In direct mock population, delicate issues present in analytic
modeling, such as scale-dependent halo bias and halo exclusion, 
are treated exactly. 
Our approach also provides a natural framework for studying 
models of assembly bias, because we can use the exact clustering 
properties of simulated halos as a function of
any arbitrary halo properties in the catalog. It is not necessary to develop 
new phenomenological models or fitting functions to deal with this additional 
complexity. With direct mock population, systematic uncertainty in the 
model is limited to the sample variance of the simulated box, errors related 
to insufficient numerical resolution, and numerical inaccuracies of 
halo-finding \citep[e.g., overmerging][]{klypin99a,rockstar}.

In addition to improvements resulting from direct mock population,
the simulation we use is based on the latest Planck cosmological
parameters \citep{planck13}, updating previous work.
Furthermore, many important differences between this work 
and the previous analysis by \citet{zehavi_etal11} result from 
the fact that the Monte Carlo Markov Chains used in \citet{zehavi_etal11} did not 
sufficiently sample the posterior distribution (Z. Zheng, private communication). 
The result is that the constraints in \citet{zehavi_etal11} are overly restrictive, considerably so 
in some cases, and potentially biased. 
Therefore, {\em our analysis supersedes previous work even in the case of
standard halo occupation models}.
